Tutorial_1a

### 2024-10-31 Tutorial_1a.Rmd
add table of content

---
title: "Tutorial_1a"
author: "Sven Panis"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: "Tutorial_1a"
author: "Sven Panis"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    theme: united
editor_options: 
  chunk_output_type: console
---
